%===============================================================================
% MINIMAL ATS-FRIENDLY CV TEMPLATE
% Author: Mihail Dobroslavski
% License: MIT
%===============================================================================

\documentclass[11pt, a4paper]{article}

%-------------------------------------------------------------------------------
% PACKAGES
%-------------------------------------------------------------------------------
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.5in]{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}

%-------------------------------------------------------------------------------
% CONFIGURATION
%-------------------------------------------------------------------------------
% Accent color (subtle dark blue, change to black for pure B&W)
\definecolor{accent}{RGB}{0, 51, 102}

% Hyperlink styling
\hypersetup{
    colorlinks=true,
    linkcolor=accent,
    urlcolor=accent,
    pdfauthor={Mihail Dobroslavski},
    pdftitle={Mihail Dobroslavski - CV}
}

% Add underline to all hyperlinks
\let\oldhref\href
\renewcommand{\href}[2]{\oldhref{#1}{\underline{#2}}}

% Remove page numbers
\pagestyle{empty}

% Section formatting
\titleformat{\section}
    {\large\bfseries\color{accent}}
    {}
    {0em}
    {}
    [\titlerule]

\titlespacing{\section}{0pt}{10pt}{6pt}

% List settings
\setlist[itemize]{
    leftmargin=1.5em,
    itemsep=1pt,
    parsep=0pt,
    topsep=2pt
}

%-------------------------------------------------------------------------------
% CUSTOM COMMANDS
%-------------------------------------------------------------------------------

% Header command
% Usage: \cvheader{Name}{Email}{GitHub}{LinkedIn}
\newcommand{\cvheader}[4]{
    \begin{center}
        {\LARGE\bfseries #1}\\[4pt]
        \href{mailto:#2}{#2} \quad | \quad
        \href{#3}{GitHub} \quad | \quad
        \href{#4}{LinkedIn}
    \end{center}
    \vspace{-4pt}
}

% Profile command
% Usage: \cvprofile{Text}
\newcommand{\cvprofile}[1]{
    \section{Profile}
    #1
}

% Experience/Project entry command
% Usage: \cventry{Title}{Organization}{Date}{Location}{Technologies}
\newcommand{\cventry}[5]{
    \noindent\textbf{#1} \hfill \textit{#3}\\
    \textit{#2} \hfill #4\\
    \textbf{Stack:} #5
    \vspace{2pt}
}

% Education entry command
% Usage: \cveducation{Degree}{Institution}{Date}{Details (optional)}
\newcommand{\cveducation}[4]{
    \noindent\textbf{#1} \hfill \textit{#3}\\
    \textit{#2}\\
    #4
}

% Skills row command
% Usage: \cvskill{Category}{Skills}
\newcommand{\cvskill}[2]{
    \noindent\textbf{#1:} #2
}

%===============================================================================
% DOCUMENT
%===============================================================================
\begin{document}

%-------------------------------------------------------------------------------
% HEADER
%-------------------------------------------------------------------------------
\cvheader
    {Mihail Dobroslavski}
    {mihail.dobroslavski@gmail.com}
    {https://github.com/MishoMish/}
    {https://www.linkedin.com/in/mihail-dobroslavski-4826b831a/}

%-------------------------------------------------------------------------------
% PROFILE
%-------------------------------------------------------------------------------
\cvprofile{
    Computer Science undergraduate with 2 years of full-stack production experience in the media sector. Strong focus on frontend development using React and TypeScript, with exposure to backend services and cloud deployment. Teaching assistant and student council member with expertise in systems programming. Open-source contributor with personal projects showcased on GitHub.
}

%-------------------------------------------------------------------------------
% SKILLS
%-------------------------------------------------------------------------------
\section{Skills}

\cvskill{Languages}{C++, TypeScript, JavaScript, SQL, HTML/CSS, Java}\\[2pt]
\cvskill{Frameworks \& Libraries}{React, Node.js, Koa, Tailwind CSS, video.js, Knex}\\[2pt]
\cvskill{Tools \& Platforms}{PostgreSQL, Docker, Azure, Git, Keycloak, Storybook}\\[2pt]
\cvskill{Concepts}{REST APIs, Authentication (JWT/OAuth), CI/CD, Infrastructure as Code, Containerization}

%-------------------------------------------------------------------------------
% EXPERIENCE
%-------------------------------------------------------------------------------
\section{Experience}

\cventry
    {Software Engineer}
    {Bulgarian National Television}
    {Jan 2024 -- Dec 2025}
    {Sofia, Bulgaria}
    {React, TypeScript, Node.js, Koa, PostgreSQL, Keycloak, Azure, Docker, Terraform}

\begin{itemize}
    \item Contributed to \textbf{BNT Play}, a national-scale VOD and streaming platform serving \textbf{20 thousand active users} across Bulgaria's broadcast infrastructure.
    \item Engineered a reusable UI component library using \textbf{Storybook} and TypeScript, standardizing the design system across the BNT Play platform.
    \item Implemented video playback utilizing \textbf{video.js}, supporting \textbf{HLS streaming} for live broadcasts and progressive MP4 delivery for on-demand content.
    \item Collaborated with a small development team to deliver production features using established Azure infrastructure and CI/CD workflows.
\end{itemize}

\vspace{4pt}

\cventry
    {Teaching Assistant}
    {Faculty of Mathematics and Informatics, Sofia University}
    {Sep 2023 -- Present}
    {Sofia, Bulgaria}
    {C++, Data Structures and Programming, OOP}

\begin{itemize}
    \item Mentored \textbf{75+ students} across 3 core CS courses, conducting weekly lab sessions and code reviews.
    \item Authored \textbf{automated test cases} for grading assignments, improving grading efficiency and consistency.
    \item Provided 1:1 mentorship on complex topics like memory management and OOP principles, helping students master foundational concepts.
\end{itemize}

%-------------------------------------------------------------------------------
% EDUCATION
%-------------------------------------------------------------------------------
\section{Education}

\cveducation
    {Bachelor of Science in Computer Science}
    {Sofia University St. Kliment Ohridski, Faculty of Mathematics and Informatics}
    {2022 -- 2026 (Expected)}
    {Relevant coursework: Data Structures, Algorithms, Operating Systems, Databases, OOP, Computer Networks}

%-------------------------------------------------------------------------------
% LEADERSHIP & COMMUNITY
%-------------------------------------------------------------------------------
\section{Leadership \& Community}

\noindent\textbf{Student Council Member} \hfill \textit{Apr 2024 -- Present}\\
\textit{Faculty of Mathematics and Informatics}
\begin{itemize}
    \item Organized \textbf{FMI Codes}, one of Bulgaria's largest student hackathons with \textbf{100+ participants} across 18 teams; led technical production for a \href{https://www.youtube.com/watch?v=UXKOYHhelAc}{7 hour live-streamed closing ceremony}.
    \item Coordinated logistics and onboarding for 300+ first-year students during \textbf{Freshers Weekend FMI Edition}.
    \item Led the organizing team for \textbf{FMI Game Olympics} tournaments across chess, board games, table tennis, and esports.
\end{itemize}

%-------------------------------------------------------------------------------
% LANGUAGES
%-------------------------------------------------------------------------------
\section{Languages}

\noindent Bulgarian (Native) \quad | \quad English (B2--C1, Professional Working Proficiency)

\end{document}
